Autonomous Realization of Simple Machines

### 2014-05-26 doc/paper/paper.tex
exps halfway done

\subsection{Designs with Different Load Weights}

To assess the ability of the proposed design algorithm, the framework is tested with two different
load sizes, 50 kg and 100 kg, where the planner needs to choose from two different levers 1.7 and 2.5
m long in each case. Once a choice is made, Golem Krang autonomously constructs the design, as
described in Section 3, and we measure the force/torque sensor readings at the end-effector of
the actuating arm. Figure \ref{fig:comparison} demonstrates the readings for the two experiments
where the maximum applied forces are 242.27 Nm and 368.63 Nm for 50 kg and 100 kg experiments
respectively. We conclude that the mechanical advantage is 2.02:1 and 2.66:1 for each case, and 
the maximum force limit is preserved; and thus, the planned design, its assembly and actuation are
successful.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.7\linewidth]{Figures/loads.png}
  \caption{The mechanical advantage in forces}
  \label{fig:comparison}
\end{figure}

\subsection{Fulcrum Base Choice and Unmodeled Implications}

>>>>

\subsubsection{Designs with Different Load Weights}

The proposed framework is tested with two 
load sizes, 50 kg and 100 kg, where the planner chooses from two levers 1.7 and 2.5
m long. Once the design is made, Golem Krang autonomously constructs it, as
described in Section 3, and we measure the force/torque sensor readings at the actuating arm gripper. Figure \ref{fig:graphs}a demonstrates the maximum applied forces at 242.27 Nm and 368.63 Nm for 50 kg and 100 kg experiments
respectively. We conclude that the mechanical advantage is 2.02:1 and 2.66:1 for each case, and 
the maximum force limit is preserved; and thus, the planned design, its assembly and actuation are
successful.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/loads.png}
  \caption{Left: Input forces during the 50 kg (red) and 100 kg (red) overturning tasks. 
  Right: Fulcrum shift while using a small lever leads to increased input force  (grey line).}

  \label{fig:graphs}
\end{figure}

\vspace{-2em}
\subsubsection{Fulcrum Base Choice and Unmodeled Implications}

The proposed planner focuses on the initial moment of force application and ensures that the force
induces enough torque to overturn the load. Although constraints are used to guarantee that the
motion is collision-free, the possibility of the the contact between
the lever and the cinder block moving is not considered. Figure \ref{fig:short}a demonstrates a case where
the planner \textit{autonomously} adapts the fulcrum base choice to accommodate the short
lever. However, the fulcrum point moves (Figures \ref{fig:short}b-c) because the contact height is
shorter than the center of mass of the load. Figure \ref{fig:graphs}b displays the increase in
the required force as the fulcrum shifts.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/short.png}
  \caption{.}
  \label{fig:short}
\end{figure}

\subsubsection{Evaluating Accuracy}

DONT READ HERE YET!

A significant challenge in accomplishing the series of the autonomous manipulation and perception
tasks has been the accumulation of error over the course of the executions. To remedy such an error
build-up, at the current state of our work, the authors intervene and instruct the robot to minimize
its position errors. We focus on the two main reasons and propose possible solutions.

During experiments, we observed that the RGBD data becomes more erroneous as the distance increases.
Within a 1 meter bound, the mean error is within 2-3 cm whereas with the maximum 4 meters (e.g. the
room limits), we see errors up to 10 cm. The proportional increase of error with respect to distance
suggest a camera calibration problem. Another source of error could be the slack in the tilt and pan
joints that control the camera view. The general of camera calibration has been addressed via bundle
adjustment in \cite{dasgupta1999making}.

A second reason we suspect that might lead to localization errors is the error accumulated while the
robot attempts to follow a velocity profile in the forward direction. Figure \ref{fig:controller} demonstrates the
reference position and velocity trajectories (green), along with the real trajectories (red). To
remedy this error, we will focus on the trajectory following techniques developed by \cite{ha1996trajectory}.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.6\linewidth]{Figures/controller.png}
  \caption{The mechanical advantage in forces}
  \label{fig:controller}
\end{figure}
